Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes

### 2013-06-15 Report/article.tex
rapport

\subsection{Intial set-up cost}
(Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold).\\
Here we estimate the performance in terms of run time for KeyGen, Encrypt, Decrypt, Add, Mult, Recrypt.

\textbf{KeyGen}\\
The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 1s].
\begin{comment}
\begin{figure}[!h] %on ouvre l'environnement figure
\centering
\includegraphics[width=5cm]{f3.eps} 
\caption{Run time of KeyGen(ms)} 
\label{image_f2} %l'étiquette pour faire référence à cette image
\end{figure}
\end{comment}

>>>>

\subsection{Intial set-up cost}
Here we mesure the performance in terms of run time for KeyGen, Encrypt, Add, Mult, Recrypt, Decrypt.\\
\begin{tabular}{|c|c|c|c|c|c|c|c|}
  \hline
  \multicolumn{8}{|c|}{$\mu = 4$} \\
  \hline
  N & $log_{2}(p)$ & KeyGen & Encrypt & Add & Mult & Recrypt & Decrypt \\
  \hline
  $2^{1}$ & 1.2 & & 1.3 & & & & \\
  $2^{2}$ & 2.2 & & 2.3 & & & & \\
  $2^{3}$ & 2.2 & & 2.3 & & & & \\
  $2^{4}$ & 2.2 & & 2.3 & & & & \\
  $2^{5}$ & 2.2 & & 2.3 & & & & \\
  \hline
\end{tabular}

\textbf{KeyGen}\\
The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 2s]\autoref{image_f2}.

\begin{figure}[!h] %on ouvre l'environnement figure
\centering
\includegraphics[width=5cm]{f3.pdf} 
\caption{Run time of KeyGen(ms)} 
\label{image_f2} %l'étiquette pour faire référence à cette image
\end{figure}
